Coherent optical creation of a single molecule

### 2020-12-01 paper.tex
Whatever

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (a) The light shift of the Raman resonance fitted to$a(P)+b(P)/\Delta$, where
    $a(P)$ and $b(P)=(\Omega_a^2-\Omega_m^2)/2$
    are tweezer power dependent background and $v'=0$ contribution
    to the light shift,
    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweer}}$ is the detuning from
    the PA resonance frequency $f_{\mathrm{PA}0}$.
    The $a(P)$s are fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
    at zero tweezer power to be $f_{R0}=770.1969(2)~\mathrm{MHz}$.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to$c(P)+d(P)/\Delta$, where
    $c(P)$ and $d(P)=\Omega_a\Omega_m/2$
    are tweezer power dependent background and $v'=0$ contribution.
    The detuning is calculated using the PA frequency fitted in (a).
    The $c(P)$s and $d(P)$s are proportional to $P^{1.29}$
    and the fit gives $c(P)/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
    and $d(P)/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz/mW^{1.29}}$.
    The fitting results for (a) and (b) are shown in table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
    $b(P)$ and $d(P)$ on a log-log scale showing the $P^{0.5}$ scaling of $\Omega_m$ and
    the $P^{0.79}$ scaling of $\Omega_a$.
    \label{f-det}}
\end{figure*}
\begin{table}[ht]
  \centering
  \begin{tabular}{|c|c|}
    $f_{\mathrm{PA}0}$&$288711.8~\mathrm{GHz}$\\\hline
    $a(0.75~\mathrm{mW})$&$770.20452(6)~\mathrm{MHz}$\\
    $b(0.75~\mathrm{mW})$&$-12.46(2)~\mathrm{MHz\cdot GHz}$\\
    $a(1.5~\mathrm{mW})$&$770.2081(1)~\mathrm{MHz}$\\
    $b(1.5~\mathrm{mW})$&$-24.44(3)~\mathrm{MHz\cdot GHz}$\\
    $a(3.75~\mathrm{mW})$&$770.1943(3)~\mathrm{MHz}$\\
    $b(3.75~\mathrm{mW})$&$-60.66(8)~\mathrm{MHz\cdot GHz}$\\\hline
    $c(0.75~\mathrm{mW})$&$-2\pi\times0.29(2)~\mathrm{kHz}$\\
    $d(0.75~\mathrm{mW})$&$-4\pi^2\times115(4)~\mathrm{kHz\cdot GHz}$\\
    $c(1.5~\mathrm{mW})$&$-2\pi\times0.63(4)~\mathrm{kHz}$\\
    $d(1.5~\mathrm{mW})$&$-4\pi^2\times275(6)~\mathrm{kHz\cdot GHz}$\\
    $c(3.75~\mathrm{mW})$&$-2\pi\times2.4(2)~\mathrm{kHz}$\\
    $d(3.75~\mathrm{mW})$&$-4\pi^2\times0.95(3)~\mathrm{MHz\cdot GHz}$\\
  \end{tabular}
  \caption{Fitting results for Fig.~\ref{f-det}(a,b).
    \label{tab:f-det:fit}}
\end{table}

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (a) The light shift of the Raman resonance fitted to$a_P+b_P/\Delta$, where
    $a_P$ and $b_P=(\Omega_a^2-\Omega_m^2)/2$
    are tweezer power dependent background and $v'=0$ contribution
    to the light shift,
    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweer}}$ is the detuning from
    the PA resonance frequency $f_{\mathrm{PA}0}$.
    The $a_P$s are fitted to a model including linear and small quadratic light shift
    \todo{which assumes $\Omega_m\gg\Omega_a$} to obtain the Raman resonance frequency
    at zero tweezer power to be $f_{R0}=770.1969(2)~\mathrm{MHz}$.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to$c_P+d_P/\Delta$, where
    $c_P$ and $d_P=\Omega_a\Omega_m/2$
    are tweezer power dependent background and $v'=0$ contribution.
    The detuning is calculated using the PA frequency fitted in (a).
    The $c_P$s and $d_P$s are proportional to $P^{1.29}$
    and the fit gives $c_P/P^{1.29}=-2\pi\times0.41(2)~\mathrm{kHz/mW^{1.29}}$
    and $d_P/P^{1.29}=-4\pi^2\times167(2)~\mathrm{kHz/mW^{1.29}}$.
    The fitting results for (a) and (b) are shown in table~\ref{tab:f-det:fit}.
    (c) Tweezer power dependency of $\Omega_m$ (top) and $\Omega_a$ (bottom) calculated from
    $b_P$ and $d_P$ on a log-log scale showing the $P^{0.5}$ scaling of $\Omega_m$ and
    the $P^{0.79}$ scaling of $\Omega_a$.
    \label{f-det}}
\end{figure*}
\begin{table}[ht]
  \centering
  \begin{tabular}{|c|c|c|c|}
    $P~(\mathrm{mW})$&$0.75$&$1.5$&$3.75$\\\hline
    $f_{\mathrm{PA}0}~(\mathrm{GHz})$&\multicolumn{3}{|c|}{$288711.8$}\\\hline
    $a~(\mathrm{MHz})$&$770.20452(6)$&$770.2081(1)$&$770.1943(3)$\\
    $b~(\mathrm{MHz\cdot GHz})$&$-12.46(2)$&$-24.44(3)$&$-60.66(8)$\\\hline
    $c~(\mathrm{2\pi\times kHz})$&$0.29(2)$&$0.63(4)$&$2.4(2)$\\
    $d~(\mathrm{4\pi^2\times MHz\cdot GHz})$&$0.115(4)$&$0.275(6)$&$0.95(3)$\\
  \end{tabular}
  \caption{Fitting results for Fig.~\ref{f-det}(a,b).
    \label{tab:f-det:fit}}
\end{table}
